A Partitioning Algorithm for Maximum Common Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-15 paper/paper.tex
s/self-loops/loops/g

\section{Extensions}\label{sec:extensions}
\paragraph{Vertex labels and self-loops} If vertices are labelled, replace ${\langle
V(G),V(H) \rangle}$ in \lineref{FirstExpandCall} with a set of label classes, one for each label that appears in both $\V(G)$ and
$\V(H)$. If vertex labels are represented as positive integers, represent self-loops
as negative integers.

@@

We have introduced the \McSplit\ algorithm for Max Common Subgraph.
The new algorithm is more than an order of
magnitude faster than the previous state of the art for unlabelled and undirected
instances. We have shown how the algorithm can be extended for graphs with labels on edges, labels on vertices, self-loops, directed edges and the requirement that the resultant graph be connected.

>>>>

\section{Extensions}\label{sec:extensions}
\paragraph{Vertex labels and loops} If vertices are labelled, replace ${\langle
V(G),V(H) \rangle}$ in \lineref{FirstExpandCall} with a set of label classes, one for each label that appears in both $\V(G)$ and
$\V(H)$. If vertex labels are represented as positive integers, represent loops
as negative integers.

@@

We have introduced the \McSplit\ algorithm for Max Common Subgraph.
The new algorithm is more than an order of
magnitude faster than the previous state of the art for unlabelled and undirected
instances. We have shown how the algorithm can be extended for graphs with labels on edges, labels on vertices, loops, directed edges and the requirement that the resultant graph be connected.
